DRAFT

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

### • Plot for diff years diff countries
```{r}
df3 <- aggregate(trueprice ~ country + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
  geom_bar(stat='identity') + facet_wrap(~country) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2)
```

@@

### • Plot for classes
```{r echo=FALSE, message=FALSE}
datasummary(trueprice*class ~ Mean, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```
```{r echo=FALSE}
ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 
  geom_bar(stat = 'summary') + labs(x='Class', y='Price', fill = 'Class')
```

>>>>

### • Plot for diff years diff countries
```{r}
df3 <- aggregate(trueprice ~ country + year, 
                 data=df2, 
                 function(x) { 
                   c(mean_price = mean(x)) 
                 })
ggplot(data = df3, aes(x=year, y=trueprice, fill=country)) + 
  geom_bar(stat='identity') + facet_wrap(~country) +
  geom_text(aes(label = round(trueprice)), vjust = -0.2) +
  scale_x_discrete() + ylim(0, 195) + 
  labs(x='Year(2017,2018)', y='Price for one night (in EUR)', fill='Country')
```

@@

### • Plot for classes
```{r echo=FALSE, message=FALSE}
datasummary(trueprice*class ~ Mean, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```
```{r echo=FALSE, message=FALSE}
ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 
  geom_bar(stat = 'summary') + labs(x='Class', y='Price for 1 night (in EUR)', fill = 'Class')
```
